---
title: "Bioconductor Utilities as RStudio Addins"
author:
- name: Marcel Ramos
  affiliation: Roswell Park Cancer Institute, Buffalo, NY
date: "`r BiocStyle::doc_date()`"
vignette: >
  %\VignetteIndexEntry{Bioconductor Utilities as RStudio Addins}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output: BiocStyle::html_document
Package: BiocAddins
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Installation

```{r setup, eval=FALSE}
BiocManager::install("Bioconductor/BiocAddins")
```

# Utility functions

## Installing BiocManager

Bioconductor uses BiocManager to distribute pacakges and manage Bioconductor
versions. It is important for users to make use of BiocManager instead of
`install.packages` in order to ensure proper package versioning.

The RStudio Addin makes it easy for users to obtain and install `BiocManager`
from CRAN.

```{r,eval=FALSE}
useBiocManager()
```

After installation of `BiocManager`, users may install a package via the
`install` function:

```{r,eval=FALSE}
BiocManager::install("Biobase")
```

# Developer section

## Run BiocCheck

Developers can run BiocCheck quite easily with the RStudio Addin from the
dropdown menu. It essentially runs:

```{r, eval=FALSE}
BiocCheck::BiocCheck()
```

We recommend using the following keyboard shortcut:

<kbd> Ctrl </kbd> / <kbd> &#x2318; </kbd> (Mac) + <kbd> shift </kbd> + <kbd> C </kbd>

## Version Bumps

BiocAddins makes it easy to bump your package's version by running the
`bumpVersion` function:

```{r,eval=FALSE}
bumpVersion()
```

Note that this will increase the `Z` version of the package by 1, a.k.a, the
patch version.

## Installing devel

Developers who wish to install the development version of Bioconductor can
do so _after_ installing `BiocManager`:

```{r, eval=FALSE}
BiocManager::install(version = "devel")
```

Developers must ensure that the correct version of R is being used.
For more information, please review the `BiocManager` package vignette.

## Session Info

```{r}
sessionInfo()
```

